# EcophyCofog Package

A package to handle routinely produced raw outputs of the CIRAS-3, MINIPAM II and PSYPRO of EcoFog's ecophysiology lab.

Package written by Tristan LAFONT RAPNOUIL and hosted on [github](https://github.com/LafontRapnouilTristan/EcophyCofog).
Can be installed running:

```
install.packages("devtools")
library(devtools)
install_github("https://github.com/LafontRapnouilTristan/EcophyCofog")
```

## Utilitaries

### Library

Used to load install (if required) and load multiple package at once.

usage:

```{r eval=F}
EcophyCofog::Library(c("pckg1","pckg2","pckg3"))
```

### NotIn

A custom operator to test the differences between vectors.

```{r eval=F}
x <- c("a","b","c")
y <- c("d","a","e")
x %notin% y
```

`[1] FALSE  TRUE  TRUE`


### xtract_legend

Store the legend of a ggplot object.

```{r eval=F}
legend <- xtract_legend(myggplot)
```

### dummy_data

Create a meaningless numeric data frame for testing things.

```{r eval=F}
data <- dummy_data(nbcol=4,nbrow=100)
```

## MiniPAM

### merge_minipam

Merge several miniPAM output files.
All files should be stored in one folder, and only them!!
See [Fluorescence] for more details.

```{r eval=F}
library(EcophyCofog)

input_path <- PATH_TO_THE_FOLDER
filename <- NAME_OF_THE_MERGED_OUTPUT

merge_minipam(input_path,filename)
```


### minipam

Take as input a csv dataframe containing output of the minipam.
For ETR and F<sub>v</sub>/F<sub>m</sub> measurements only.
And return clean files containing each type of measurements + the ETR curves.

```{r eval=F}
library(EcophyCofog)

Name_of_the_input_file <- NAME_OF_YOUR_MERGED_FILE
input_path <- PATH_TO_SAID_FILE
path_to_ID_match <- PATH_TO_YOUR_ID_MATCH_FILE

minipam(Name_of_the_input_file,
            input_path,
            path_to_ID_match)
```


## CIRAS-3

### merge_ciras

Used to merge all ciras output of a foled into one file.

path_to_xls a character string with your path to all your ciras `.xls` output.
Their name must always end as _treatment_sampleID.xls (e.g. CIRAS_3_Aechmea m _DP_1.xls).
Skip: the number of useless rows at the top of your `.xls` file, Jean-Yves Goret template have three.

```{r eval=F}
merge_ciras(path_to_xls, skip=3)
```


## PSYPRO

### psypro


## PASCO

### PASCO_transfo

### PASCO_transfo2


## PCR layout

### plate_layout

### tag_layout